FTLR proof cases

### 2018-03-22 fully-abstract-comp/ftlr-proof-cases.tex
xjmp case was missing in proposed refactoring.
changes

{\color{DarkGreen}
\dominique{Proposed proof refactoring below:}
First, we prove that one of the following holds:
\begin{itemize}
\item $\Phi_S \step \failed$ and $\Phi_T \step\failed$
\item $\Phi_S \step \halted$ and $\Phi_T \step\halted$
\item All of the following hold:
  \begin{itemize}
  \item $\callCond{\Phi_S,r_1,r_2,\aaddr}$
  \item $\baddr \leq \aaddr \tand \aaddr + \calllen-1 \leq \eaddr$
  \item $\exec{\Phi_S(\pcreg)}$
  \item for all $i = 0..\calllen-1$, $\ms_T(\aaddr+i) = \ms_S(\aaddr+i) \in \ints$.
  \item TODO: other useful info
  \end{itemize}
\item All of the following hold: (includes simple cases: gettype, geta, getb, gete, getp, getl, lt, plus, minus, that can be handled uniformly)
  \begin{itemize}
  \item $\Phi_S \step \Phi_S'$
  \item $\Phi_T \step \Phi_T'$
  \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r}{z}} \neq \failed$
  \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r}{z}} \neq \failed$
  \item $z \in \ints$
  \end{itemize}
\item All of the following hold: (includes cap-manipulation cases: move, cca, restrict, seta2b, cseal, split, splice, that can be handled mostly uniformly)
  \begin{itemize}
  \item \item $\Phi_S \step \Phi_S'$
  \item $\Phi_T \step \Phi_T'$
  \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r_1\cdots r_k}{w_1\cdots w_k}}\neq \failed$
  \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r_1\cdots r_k}{w_1'\cdots w_k'}} \neq \failed$
  \item One of the following holds:
    \begin{itemize}
    \item (restrict,cca,seta2b) $w_1 = ((\perm,\lin),\baddr,\eaddr,\aaddr)$, $w_2 = ((\perm,\lin),\baddr,\eaddr,\aaddr)$, $\Phi_S(r_1) = ((\perm',\lin),\baddr,\eaddr,\aaddr')$ and $\Phi_T(r_1) = ((\perm',\lin),\baddr,\eaddr,\aaddr')$ and $\perm' \sqsubseteq\perm$,
      $k = 1$
    \item (restrict,cca,seta2b) $w_1 = \stkptr{\perm,\baddr,\eaddr,\aaddr}$, $w_2 = ((\perm,\lin),\baddr,\eaddr,\aaddr)$, $\Phi_S(r_1) = \stkptr{\perm',\baddr,\eaddr,\aaddr'}$ and $\Phi_T(r_1) = ((\perm',\lin),\baddr,\eaddr,\aaddr')$ and $\perm' \sqsubseteq\perm$,
      $k = 1$
    \item ...
      \end{itemize}
  \end{itemize}
\item Other cases: store, load, jmp, jnz
\end{itemize}

@@

\end{proof}
\end{document}

>>>>

{\color{DarkGreen}
\dominique{Proposed proof refactoring below:}
First, we prove that one of the following holds:
\begin{itemize}
\item $\Phi_S \step \failed$ and $\Phi_T \step\failed$
\item $\Phi_S \step \halted$ and $\Phi_T \step\halted$
\item All of the following hold:
  \begin{itemize}
  \item $\callCond{\Phi_S,r_1,r_2,\aaddr}$
  \item $\baddr \leq \aaddr \tand \aaddr + \calllen-1 \leq \eaddr$
  \item $\exec{\Phi_S(\pcreg)}$
  \item for all $i = 0..\calllen-1$, $\ms_T(\aaddr+i) = \ms_S(\aaddr+i) \in \ints$.
  \item TODO: other useful info
  \end{itemize}
\item All of the following hold: (includes simple cases: gettype, geta, getb, gete, getp, getl, lt, plus, minus, that can be handled uniformly)
  \begin{itemize}
  \item $\Phi_S \step \Phi_S'$
  \item $\Phi_T \step \Phi_T'$
  \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r}{z}} \neq \failed$
  \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r}{z}} \neq \failed$
  \item $z \in \ints$
  \end{itemize}
\item All of the following hold: (includes cap-manipulation cases: move, cca, restrict, seta2b, cseal, split, splice, that can be handled mostly uniformly)
  \begin{itemize}
  \item \item $\Phi_S \step \Phi_S'$
  \item $\Phi_T \step \Phi_T'$
  \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r_1\cdots r_k}{w_1\cdots w_k}}\neq \failed$
  \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r_1\cdots r_k}{w_1'\cdots w_k'}} \neq \failed$
  \item One of the following holds:
    \begin{itemize}
    \item (restrict,cca,seta2b) $w_1 = ((\perm,\lin),\baddr,\eaddr,\aaddr)$, $w_2 = ((\perm,\lin),\baddr,\eaddr,\aaddr)$, $\Phi_S(r_1) = ((\perm',\lin),\baddr,\eaddr,\aaddr')$ and $\Phi_T(r_1) = ((\perm',\lin),\baddr,\eaddr,\aaddr')$ and $\perm' \sqsubseteq\perm$,
      $k = 1$
    \item (restrict,cca,seta2b) $w_1 = \stkptr{\perm,\baddr,\eaddr,\aaddr}$, $w_2 = ((\perm,\lin),\baddr,\eaddr,\aaddr)$, $\Phi_S(r_1) = \stkptr{\perm',\baddr,\eaddr,\aaddr'}$ and $\Phi_T(r_1) = ((\perm',\lin),\baddr,\eaddr,\aaddr')$ and $\perm' \sqsubseteq\perm$,
      $k = 1$
    \item ...
      \end{itemize}
  \end{itemize}
\item Other cases: store, load, jmp, jnz, xjmp
\end{itemize}

@@

\end{proof}

\begin{lemma}[call lemma]

\end{lemma}

\section{TODO/Notes}
\begin{itemize}
\item Boundary crossing can occur on jump, xjump, call \emph{and} step!
  \begin{itemize}
  \item Make a lemma for updatePc that handles the latter once and for all. Maybe make a general lemma for all boundary crossings
    \begin{itemize}
    \item updatePc special case
    \item argue about boundary crossing, trusted/untrusted, sanity conditions
    \end{itemize}
  \end{itemize}
\item Lemma about call
\end{itemize}
\end{document}
